The human in the loop: volunteer-based metacomputers as a socio-technical system

### 2016-04-24 Alife16/paper.tex
Reviewing revision by @mariosky
And changing it a bit to avoid confusion. Closes #113.

\begin{table}[htb]
\caption{Experiment table, with summary of results. \label{tab:runs}}
\begin{center}
\begin{tabular}{l|rrl}
\hline
Experiment & \#Runs & Different IPs & Traps \\
\hline
April 4th 4/4 & 57 & 191 & 40 \\
April 24th 4/24 &  231 & 559& 40  \\
July 31th 7/31 & 97 & 179 & 40 \\
\hline
February, cache=128 & 61 & 75 & 50  \\
February, cache=64 & 61 & 220 & 50  \\
February, cache=32 & 39 & 86 & 50  \\
% grep start ~/Code/splash-volunteer/data/2016/nodio-2016-2-28-cache=32.log
\hline
\end{tabular}
\end{center}
\end{table}
%
Initial experiments were set up using the OpenShift
PaaS \url{www.openshift.com}, which provides a free tier, making the whole experiment cost
equal to \$0.00. Experiments were
announced through a series of posts on Twitter and, in the latest case, Telegram, and
results were published in\citep{DBLP:conf/gecco/GuervosG15}. For the
purpose of this paper, we repeated the announcement several times
through the month of February. All  %% April --> January ??
in all, we have the set of runs with the characteristics shown in
Table \ref{tab:runs}. In general, every experiment took several
days. No particular care was taken about the time of the announcement
%Pablo: but it would great at least describe how many times was announced and how long
or the particular wording. Every {\em experiment} consisted in running
until the solution of the 50-trap problem was found. When the correct
solution was sent to the server, the counter was updated and the pool
of solutions resets to the void set. There was no special intention to wait
until all clients had finished, thus it might happen that. In fact,
the islands running in the browser {\em spill} from one experiment to
the next. 
%However, previous experiments have proven that the influence
%of these islands in the next experiment is indeed negligible. %Pablo: cite
If and individual that is close or even at optimum value is stored in the cache 
the next experiment will be affected, because it will require less time 
to finish, this problem has been addressed in later versions of the system. 
But time to solutions is not the important measure here, is the computational
power of system established by the number of volunteers, in this measure 
previous experiments have proven that the influence
of these islands in the next experiment is indeed negligible.

The table shows that every run included more than 30 experiments. The
%Pablo: reference to table? (maybe the final print will misplace it)
number of different IPs intervening in them varied from more than one
hundred to more than five hundred in the second experiment, with a
number around 50 in the second, and most recent, batch of experiments. 
%
\begin{table}[htb]
\caption{Summary of time per run, number of IPs and number of {\tt
    PUT}s per IP in the initial runs. \label{tab:summary:os}}
\begin{center}
\begin{tabular}{l|cccc}
\hline
     & \multicolumn{2}{c}{IPs} & \multicolumn{2}{c}{Median} \\
Experiment & Median & Max & time (s) &  \#{\tt  PUT}s \\
\hline
4/4 & 5 & 16 & 2040 & 18   \\
4/24 &  5 & 29 & 732 & 11  \\
7/31 & 5 & 14 & 260 & 23   \\
\hline
Cache=128 & 5 & 17 & 222.2 & 124 \\ 
Cache=64 & 8 & 38 & 51.3 & 100 \\
Cache=32 & 6 & 19 & 58.9 & 45 \\
\hline
% Data in .RData file in Splash-volunteer
\end{tabular}
\end{center}
\end{table}
%

>>>>

\begin{table}[htb]
\caption{Experiment table, with summary of results. \label{tab:runs}}
\begin{center}
\begin{tabular}{l|rrl}
\hline
Experiment & \#Runs & Different IPs & Traps \\
\hline
April 4th 4/4 & 57 & 191 & 40 \\
April 24th 4/24 &  231 & 559& 40  \\
July 31th 7/31 & 97 & 179 & 40 \\
\hline
February, cache=128 & 61 & 75 & 50  \\
February, cache=64 & 61 & 220 & 50  \\
February, cache=32 & 39 & 86 & 50  \\
% grep start ~/Code/splash-volunteer/data/2016/nodio-2016-2-28-cache=32.log
\hline
\end{tabular}
\end{center}
\end{table}
%
Initial experiments were set up using the OpenShift
PaaS \url{www.openshift.com}, which provides a free tier, making the whole experiment cost
equal to \$0.00. Experiments were
announced through a series of posts on Twitter and, in the latest case, Telegram, and
results were published in\citep{DBLP:conf/gecco/GuervosG15}. For the
purpose of this paper, we repeated the announcement several times
through the month of February. All  %% April --> January ??
in all, we have the set of runs with the characteristics shown in
Table \ref{tab:runs}. In general, every experiment took several
days. No particular care was taken about the time of the announcement
%Pablo: but it would great at least describe how many times was announced and how long
or the particular wording. Every {\em experiment} consisted in running
until the solution of the 50-trap problem was found. When the correct
solution was sent to the server, the counter was updated and the pool
of solutions resets to the void set. There was no special intention to wait
until all clients had finished, thus it might happen that. In fact,
the islands running in the browser {\em spill} from one experiment to
the next. 
If an individual that is close or even at optimum value is stored in the cache 
the next experiment will be affected, and it will require less time 
to finish. This problem has been addressed in later versions of the
system, however, time to solution is not the important measure here,
where we are concerned with the computational 
power of the system established by the number of volunteers.

The table shows that every experiment included more than 30 runs. The
%Pablo: reference to table? (maybe the final print will misplace it)
number of different IPs intervening in them varied from more than one
hundred to more than five hundred in the second experiment, with a
number around 50 in the second, and most recent, batch of experiments. 
%
\begin{table}[htb]
\caption{Summary of time per run, number of IPs and number of {\tt
    PUT}s per IP in the initial runs. \label{tab:summary:os}}
\begin{center}
\begin{tabular}{l|cccc}
\hline
     & \multicolumn{2}{c}{IPs} & \multicolumn{2}{c}{Median} \\
Experiment & Median & Max & time (s) &  \#{\tt  PUT}s \\
\hline
4/4 & 5 & 16 & 2040 & 18   \\
4/24 &  5 & 29 & 732 & 11  \\
7/31 & 5 & 14 & 260 & 23   \\
\hline
Cache=128 & 5 & 17 & 222.2 & 124 \\ 
Cache=64 & 8 & 38 & 51.3 & 100 \\
Cache=32 & 6 & 19 & 58.9 & 45 \\
\hline
% Data in .RData file in Splash-volunteer
\end{tabular}
\end{center}
\end{table}
%
